Ultrafast Electron Microscopes: Design Criteria, Electron Sources, and Column Modeling

### 2013-04-05 inc/model_results/introduction.tex
more tweaks to model_results

The examples presented will each use one of two initialization schemes.
The first represents an idealized pulse which is not generated by photocathode and then accelerated, but rather springs into existence at its initial position with its velocity already established.
This type of pulse is useful to demonstrate general pulse dynamics or the ideal influence of electron-optical elements independent of the pulse's creation conditions.
Simulations using pulses of this type will provide an initial velocity $v_{\smallzero}$ (or equivalent acceleration voltage $V_{DC}$), an excess photoemission energy $\Delta E$, and HW1/eM dimensions; width $w$ and duration $\tau$ or length $ w_z = v_{\smallzero} \tau$.
The width and length will be used directly to calculate initial spatial variances $\sigma_{\alpha}$.
Both momentum chirp terms, $\gamma_{\alpha}$, will be initially zero, but since pulses must still be subject to Liouville's Theorem (discussed in Section \ref{sec:liouville}), \ref{eq:summary} will still be used to calculate meaningful local momentum widths $\eta_{\alpha}$.
This idealization only applies to the initialization, therefore these pulses will still be subject to intrinsic pulse broadening and internal space-charge repulsion which might cause pulse expansion before or during the demonstration, especially for high charge densities.

>>>>

The examples presented will each use one of two initialization schemes.
The first represents an idealized pulse which is not generated by photocathode and then accelerated, but rather springs into existence at its initial position with its velocity already established.
This type of pulse is useful to demonstrate general pulse dynamics or the ideal influence of electron-optical elements independent of the pulse's creation conditions.
Simulations using pulses of this type will provide an initial velocity $v_{\smallzero}$ (or equivalent acceleration voltage $V_{DC}$), an excess photoemission energy $\Delta E$, and HW1/eM dimensions; width $w_{\smallT}$ and duration $\tau$ or length $ w_z = v_{\smallzero} \tau$.
The width and length will be used directly to calculate initial spatial variances $\sigma_{\alpha}$.
Both momentum chirp terms, $\gamma_{\alpha}$, will be initially zero, but since pulses must still be subject to Liouville's Theorem (discussed in Section \ref{sec:liouville}), \ref{eq:summary} will still be used to calculate meaningful local momentum widths $\eta_{\alpha}$.
This idealization only applies to the initialization, therefore these pulses will still be subject to intrinsic pulse broadening and internal space-charge repulsion which might cause pulse expansion before or during the demonstration, especially for high charge densities.

### 2013-04-05 inc/model_results/spacecharge/spacecharge.tex
more tweaks to model_results

As seen in Section \ref{sec:initial_shapes}, at low pulse charge densities, the propagation dynamics should be largely determined by the effects associated with the intrinsic geometric pulse broadening; for most photoemission processes this is related to the excess photoemission energy $\Delta E$.
On the other hand, space-charge effects are expected to dominate at large pulse charge densities.
A full analysis of how high the charge density may be before deleterious space-charge become unmanagable would be a sizable task.
While much discussion could be had on the degree of distortion allowable as well as considerations of the initial shape of the pulse and length and arrangement of the column and its constituent elements, a certain amount of intuition can be gained simply by considering a progressive series of examples.

@@

The expected trend is evident in \ref{fig:spacecharge_noacc} which presents the predicted HW1/eM pulse width $\sqrt{2 \sigma_{\smallT}}$ (solid line) and longitudinal length $\sqrt{2 \sigma_{z}}$ (dashed line) after a propagation distance of 15cm as a function of the number of electrons in the pulse.
Once again, this simulation employs the idealistic pulse described earlier, starting with a velocity of $c/3$ (where $c$ is the speed of light in a vacuum), initial width of 1 mm, HW1/eM pulse duration 1 ps, and an excess photoemission energy $\Delta E = $ 0.5 eV.
For these conditions, used to isolate the behavior of a propagating pulse from its creation environment, the simulations clearly indicate that both the electron beam width and length at the end of the simulation will remain unchanged below about $10^5$ electrons/pulse; that is, global space-charge effects only significantly influence the pulse propagation for pulses having more than $10^5$ electrons/pulse.
In the absence of space-charge effects, the presented oblate shaped pulses should be maintained as such during unforced propagation because the initial values of the electron pulse' divergence and temporal broadening rate are both proportional to $\Delta E^{1/2}$ but not to $N$.

>>>>

As seen in Section \ref{sec:initial_shapes}, at low pulse charge densities, the propagation dynamics should be largely determined by the effects associated with the intrinsic geometric pulse broadening; for most photoemission processes this is related to the excess photoemission energy $\Delta E$.
On the other hand, space-charge effects are expected to dominate at large pulse charge densities.
A full analysis of how high the charge density may be before deleterious space-charge become unmanagable would be a sizable task.
While much discussion could be had on the degree of distortion allowable, as well as considerations of the initial shape of the pulse and length, and arrangement of the column and its constituent elements, a certain amount of intuition can be gained simply by considering a progressive series of examples.

@@

The expected trend is evident in \ref{fig:spacecharge_noacc} which presents the predicted HW1/eM pulse width $\sqrt{2 \sigma_{\smallT}}$ (solid line) and longitudinal length $\sqrt{2 \sigma_{z}}$ (dashed line) after a propagation distance of 15cm as a function of the number of electrons in the pulse.
Once again, this simulation employs the idealistic pulse described earlier, starting with a velocity of $c/3$ where $c$ is the speed of light in a vacuum (1.5ns total propagation time), initial width of 1 mm, HW1/eM pulse duration 1 ps, and an excess photoemission energy $\Delta E = $ 0.5 eV.
For these conditions, used to isolate the behavior of a propagating pulse from its creation environment, the simulations clearly indicate that both the electron beam width and length at the end of the simulation will remain unchanged below about $10^5$ electrons/pulse; that is, global space-charge effects only significantly influence the pulse propagation for pulses having more than $10^5$ electrons/pulse.
In the absence of space-charge effects, the presented oblate shaped pulses should be maintained as such during unforced propagation because the initial values of the electron pulse' divergence and temporal broadening rate are both proportional to $\Delta E^{1/2}$ but not to $N$.
